Calculating life expectancy and exploring missingness

### 2016-11-04 Code/1_Explore_Data_v2.Rmd

#first, create list of stratum.ids for each race-sex combination
for (rs in unique(levels(dat.clean$RaceSex))) {
  assign(paste0(gsub(" ", "", rs), ".stratum.ids"), 
         dat.clean %>% filter(dat.clean$RaceSex == rs) %>%
         select(StateYearRaceSex, StateYearSex, Sex2, State2, Year3) %>%
         group_by(StateYearRaceSex, StateYearSex) %>%
         filter(row_number() == 1)
         )

>>>>

#first, create list of stratum.ids for each race-sex combination
for (rs in unique(levels(dat.clean$RaceSex))) {
  assign(paste0(gsub(" ", "", rs), ".stratum.ids"), 
         dat.clean %>% filter(RaceSex == rs) %>%
         select(StateYearRaceSex, StateYearSex, Sex2, State2, Year3) %>%
         group_by(StateYearRaceSex, StateYearSex) %>%
         filter(row_number() == 1)
         )
